---
title: "Lab 08 Markdown Practice"
author: "Kelly Carscadden"
date: '2017-03-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Problem 2 from Lab 07: Logistic growth model

####Write a function of the logistic growth model (with default arguments) that plots and returns the results.

```{r localSetup}
setwd("/Users/kellycarscadden/Documents/EBIOcourses/CompBioLabsAndHomework/Lab08/")
```

####Key to parameters
start = initial population size (aka, n[1])  
timeSteps = total number generations  
r = intrinsic population growth rt  
K = carrying capacity

```{r logisticGrowth}
#Create function with default values
logGrowthFunc <- function(start = 10, timeSteps = 100, r = 0.8, K = 1000) {
  
  n <- c(start, rep(NA, timeSteps-1)) #pre-allocate, and load in starting population size
  
  for(t in 2:timeSteps) {
    n[t] <- n[t-1] + (r * n[t-1] * (K - n[t-1]) / K) #Calculate logistic growth
  }#end for loop
  
  #create data frame with time and abund
  abundDat <- data.frame("generations" = 1:timeSteps, "abundance" = n)

  #plot the data
  plot(abundDat$generations, abundDat$abundance, type = "l", col = "blue",
       xlab = "Generation", ylab = "Abundance", main = "Logistic population growth")
  
  #create a source-able file of the parameter values used 
  sink("Parameters.R")
  cat(paste("#Parameters used in discrete-time logistic growth model model run on ",
            date(),"\n"))
  cat("#Initial abundance \n")
  cat(paste("start <- ", start, "\n", sep=""))
  
  cat("#Total generations \n")
  cat(paste("timeSteps <- ", timeSteps, "\n", sep=""))
  
  cat("#Intrinsic population growth rate \n")
  cat(paste("r <- ", r, "\n", sep=""))
  
  cat("#Carrying capacity \n")
  cat(paste("K <- ", K, "\n", sep=""))
  sink()
  
  #output the data and exit the function
  return(abundDat) 
  
}#end function

#Call the function, save abundance data, and produce a plot
logGrowthResults <- logGrowthFunc()
```

####Safe write the results, preventing accidental overwriting

Attribution for mySafeWriteCSV function: Samuel Flaxman

To run and create a .csv file, remove 'eval=F' from line 58 in .Rmd.
Change the file name as desired when you call mySafeWriteCSV.
```{r dataExport, eval=F}
mySafeWriteCSV <- function(data = NULL, namebase = NULL, writeRowNames = F) {
  if(is.null(namebase)) { #check if a file name was provided
    warning("Error - no file name given!\n")
  } else if (is.null(data)) { #check if data were provided
      warning("Error - no data given!\n")
  } else {
    #remove file extension if present
    namebase <- strsplit(namebase, "\\.")[[1]][1]
    
    #create a first name to try with extension
    filename <- paste(namebase, ".csv", sep="")
    
    #create a variable to make new names in a logical sequence
    counter <- 1
    
    #use a while loop to find an unused name
    while(file.exists(filename)) {
      filename <- paste(namebase, counter, ".csv", sep="")
      counter <- counter + 1
    }#end of while
    
    cat(paste("Writing file to '", filename, "'\n", sep=""))
    
    #write the data to a file
    write.csv(data, filename, row.names = writeRowNames)
    }#end of if-else
}#end of function

mySafeWriteCSV(logGrowthResults, "Carscadden_Lab8_LogisticGrowthData")
```
